To log or not to log

### 2022-01-31 main.tex

\paragraph{Describing features of the data}
Across all time points and locations, the mean number of cases (deaths) observed was 22811 (368) with a standard deviation of 47135 (831). 
FIT A NEGATIVE BINOMIAL TO THESE OBSERVATIONS

>>>>

\paragraph{Describing features of the data}
Across all time points and locations, the mean number of cases (deaths) observed was 22811 (368) with an overall standard deviation of 47135 (831). The number of observed value does not only differ by forecast target, but also shows considerable heterogeneity by location (see Figure \ref{fig:HUB-mean-locations}. Across the different locations, the variance in observed values is roughly equal to the square of the mean, suggesting that, for a given location, both cases and deaths are not poisson-distributed, but rather exhibit over-dispersion. 
MAYBE FIT A NEGATIVE BINOMIAL TO THESE OBSERVATIONS

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-mean-obs-location.png}
    \caption{CAPTION}
    \label{fig:HUB-mean-locations}
\end{figure}

\paragraph{Features of the scores}
